Pigeons.jl: Distributed sampling from intractable distributions

### 2024-05-28 paper/PT.tex
Pass on the distributed pseudo-code

\medskip 
In this section we assume a basic understanding of 
Markov chain Monte Carlo (MCMC) methods.
For readers unfamiliar with MCMC, it is important to know that 
it is a method to obtain approximate samples from a distribution. 
More specifically, it is a class of algorithms for simulating a Markov chain of 
states that look like draws from the target distribution $\pi$.
However, with traditional 
MCMC methods, the samples may be heavily correlated instead of independent 
and may fail to sufficiently explore the 
full space of the distribution (see \cref{fig:bimodal}); 
PT is a method that aims to address these issues.
For a more in-depth review of PT, we refer readers to \cite{surjanovic2022vpt}.

@@

\subsection{Local exploration and communication}
A struct that is useful for the implementation of PT is the \texttt{Replica}, 
which we will often refer to in the remainder of this section. 
A single \texttt{Replica} struct stores a \texttt{state} variable and a \texttt{chain} 
integer, among other entries. 
At the beginning of PT, $N$ \texttt{Replicas} are created, 
one for each distribution on the annealing path, and 
the chain entries in the $N$ replicas are initialized at $1,2,\ldots,N$, respectively. 
For a given \texttt{Replica}, if the \texttt{chain} number is $i$ and the \texttt{state}
is $x$, then this means that the sample corresponding to the $i$-th distribution in 
the sequence $\pi_1, \ldots, \pi_N$ is currently at location $x$.

@@

\subsection{Distributed implementation}
A distributed implementation of PT is presented in \cref{alg:distributed_PT}
and we describe the details of the implementation below.
We present the algorithm from the perspective that the number of machines available 
is equal to the number of \texttt{Replica}s and distributions, $N$. 
However, Pigeons.jl also allows for the more general case where the number of 
machines is not necessarily equal to $N$.

\subsubsection{The \texttt{PermutedDistributedArray}}
\label{sec:permuted_dist_array}
Recall that our theoretical $O(1)$ message size for communication between two machines 
is achieved by exchanging \texttt{chain} indices between \texttt{Replica}s 
instead of their \texttt{state}s.
One difficulty can be encountered in a distributed implementation, which we 
illustrate with the following simple example. 
Suppose we have $N=4$ distributions, chains, replicas, and machines, and that 
machine 1 is exploring chain 2 while machine 4 is exploring chain 3.
At one point, the \texttt{Replica} at \texttt{chain} 2 (machine 1) might need to exchange
\texttt{chain} indices with the \texttt{Replica} that has \texttt{chain} index 3 (machine 4). 
However, a priori it is not clear how machine 1 should know that it should communicate 
with machine 4 because it has no knowledge about the chain indices on the other machines.

\medskip 
To resolve this issue, we introduce a special data structure called a 
\texttt{PermutedDistributedArray}. In the case where the number of replicas is 
equal to the number of available machines, the construction is quite simple
and effectively results in each machine storing one additional integer. 
Considering the same example above, the solution to the problem is to have
machine 1 (\texttt{chain} 2 wanting to communicate with \texttt{chain} 3) 
communicate with \textit{machine} 3. 
Machine 3 stores in its \texttt{dist\_array} variable of type 
\texttt{PermutedDistributedArray} the value 4, which is the machine number that 
stores \texttt{chain} 3. By updating these \texttt{PermutedDistributedArray} 
variables at each communication step, we can ensure that each machine $j$ is aware 
of which machine number currently stores \texttt{chain} $j$. 
Therefore, the machines act as keys in a dictionary for the communication 
permutations.
An illustration of communication between four machines is provided in 
\cref{fig:index_process}.
We note that with a \texttt{PermutedDistributedArray} we make special assumptions 
on how we access and write to the array elements. 
Several MPI processes cooperate, with each machine storing 
data for a slice of this distributed array, and at each time 
step an index of the array is manipulated by exactly one machine.
% With these assumptions we achieve read/write costs that are 
% near-constant in the number of machines participating.

\begin{figure*}[t] 
  \centering 
  \begin{minipage}{0.48\textwidth}
    \centering
    \includegraphics[width=0.39\textwidth]{../img/Communication_1_v3.pdf}
    \includegraphics[width=0.59\textwidth]{../img/index_process_1.pdf}
  \end{minipage}
  \begin{minipage}{0.48\textwidth}
    \centering
    \includegraphics[width=0.39\textwidth]{../img/Communication_2_v3.pdf}
    \includegraphics[width=0.59\textwidth]{../img/index_process_2.pdf}
  \end{minipage}
  \begin{minipage}{0.48\textwidth}
    \centering
    \includegraphics[width=0.39\textwidth]{../img/Communication_3_v3.pdf}
    \includegraphics[width=0.59\textwidth]{../img/index_process_3.pdf}
  \end{minipage}
  \begin{minipage}{0.48\textwidth}
    \centering
    \includegraphics[width=0.39\textwidth]{../img/Communication_4_v3.pdf}
    \includegraphics[width=0.59\textwidth]{../img/index_process_4.pdf}
  \end{minipage}
  \caption{
    A summary of communication between four machines with $N=4$ PT chains.
    Circles represent machines with the machine number in the center of the circle. 
    Different colours are also used for different machines.
    Numbers in parantheses represent the \texttt{chain} 
    that is currently being explored by that machine. 
    Arrows indicate communication occuring between machines to exchange \texttt{chain} 
    indices.
    To keep track of which chains are stored on which machine, we introduce the 
    \texttt{dist\_array} of type \texttt{PermutedDistributedArray}, described in 
    \cref{sec:permuted_dist_array}, which is of length $N$. 
    The $j$-th element of \texttt{dist\_array} at a given time step indicates which 
    machine number is storing \texttt{chain} index $j$.
    The bolded curve in the figures to the right indicate the trajectory of the first 
    \texttt{Replica} over the course of each of the communication steps.      
    \textbf{Top left:} the PT replicas are initialized and the first communication step 
    is proposed. At this time step, $\texttt{dist\_array} = [1,2,3,4]$.
    \textbf{Top right:} after the first successful communication step, we now have 
    $\texttt{dist\_array} = [2,1,4,3]$.
    \textbf{Bottom left:} The second communication step is completed and 
    $\texttt{dist\_array} = [2,4,1,3]$.
    \textbf{Bottom right:} The third communication step is completed and 
    $\texttt{dist\_array} = [4,2,3,1]$.}
  \label{fig:index_process}
\end{figure*}

\subsubsection{MPI implementation details}
We use the MPI.jl \cite{byrne2021mpi} package to support communication between machines. 
In our pseudocode in \cref{alg:distributed_PT} we define the MPI-style 
functions \texttt{send()}, \texttt{receive!()}, 
and \texttt{waitall()}. 
The function \texttt{send()} has three arguments in our pseudocode: the first argument 
is the object to be sent, the second is the machine number to which the object should 
be sent, and finally the third argument is a unique tag for this specific send/receive 
request at this time step and on this machine, generated by \texttt{tag()}.
The \texttt{tag()} function can be any function that allows one to uniquely identify 
a tag for a given send/receive request on a given machine at any given time step $t$.
The function \texttt{receive!()} has the same last two arguments as \texttt{send()} 
except that the first argument 
specifies the object to which data should be written directly. Finally, 
\texttt{waitall(requests)} waits for all initialized MPI \texttt{requests} for a given pair 
of machines to complete.

\medskip 
In \cref{alg:distributed_PT} we also introduce the functions 
\texttt{permuted\_get()} and \texttt{permuted\_set!()}. 
Given the current machine's \texttt{dist\_array} and the 
\texttt{partner} chain with which it should communicate, 
\texttt{permuted\_get()} returns the machine number that holds the \texttt{partner} chain. 
Given the current machine's \texttt{dist\_array}, \texttt{chain} number, and machine number $j$,
\texttt{permuted\_set!()} updates the \texttt{PermutedDistributedArray} variables 
with the updated permutation.

@@

      \State $x_t \gets \texttt{local\_exploration}(\pi_\texttt{chain}, x_{t-1})$
      \State $\texttt{partner} \gets \texttt{nothing}$
      \If{$\texttt{chain} \in P$}
        \State $\texttt{partner} \gets \texttt{chain}+1$
      \ElsIf{$\texttt{chain}-1 \in P$}
        \State $\texttt{partner} \gets \texttt{chain}-1$
      \EndIf
      \If{$\texttt{partner != nothing}$ \textbf{and} \text{swap is accepted}}
        \State $\texttt{to\_machine} \gets \texttt{permuted\_get}(\texttt{dist\_array}, \texttt{partner})$
          \Comment{retrieve \texttt{dist\_array}[\texttt{partner}]}
        \State $\texttt{send\_tag} \gets \texttt{tag}(t, \texttt{chain}, j)$
        \State $\texttt{send}(\texttt{chain}, \texttt{to\_machine}, \texttt{send\_tag})$
        \State $\texttt{receive\_tag} \gets \texttt{tag}(t, \texttt{chain}, \texttt{to\_machine})$
        \State $\texttt{receive!}(\texttt{chain}, \texttt{to\_machine}, \texttt{receive\_tag})$
        \State $\texttt{waitall(requests)}$ 
          \Comment{wait for MPI requests for this pair of machines to complete}
        \State $\texttt{permuted\_set!}(\texttt{dist\_array}, \texttt{chain}, j)$
          \Comment{set value of \texttt{dist\_array}[\texttt{chain}] to \texttt{to\_machine}}
      \EndIf
      \State $c_t \gets \texttt{chain}$ 
		\EndFor
    \State \Return $\{(x_t, c_t)\}_{t=1}^T$
	\end{algorithmic}
  \caption{Distributed PT on machine $j$ (one replica per machine)}
  \label{alg:distributed_PT}
\end{algorithm}

@@

\begin{figure*}[t]
    \centering
    \begin{minipage}{0.4\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../img/speedup_distributed.pdf}
    \end{minipage}
    \begin{minipage}{0.4\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../img/speedup_parallel.pdf}
    \end{minipage}
    \caption{
        Weak scaling results for PT in both the distributed (MPI) and parallel settings 
        with approximate 95\% confidence intervals for the speedup.  
        The blue dotted line represents a hypothetical speedup equal to the 
        number of processes/threads. 
        The red dashed line indicates a speedup of one for reference.
        \textbf{Left:} Distributed setup. 
        \textbf{Right:} Parallel (shared memory) setup. 
    }
    \label{fig:PT_scaling}
\end{figure*}

@@

We emphasize again that Pigeons supports both shared memory 
parallelism (SMP) and distributed memory parallelism (DMP). However, in certain cases, it 
might be useful to run parallel tempering with very many chains or 
to run several instances of parallel tempering at once. In such cases, 
the DMP setup is the most natural if the requested number of chains is very large. 
Another notable example of the benefit of DMP is for the multi-GPU use case. 
For instance, in some situations the likelihood evaluation of a single chain may 
require its own GPU (e.g., if one is running a Fast Fourier Transform on a GPU). 
Additionally, DMP can be useful when the user's code is not thread safe. 
In such cases, concurrency can still be achieved via DMP.
Our implementation in Pigeons ensures that the 
communication cost in the DMP setup is minimal. In most cases, the 
communication cost is negligible compared to other computations performed on each process.

>>>>

\medskip 
In this section we assume a basic understanding of 
Markov chain Monte Carlo (MCMC) methods.
For readers unfamiliar with MCMC, it is important to know that 
it is a method to obtain approximate samples from a distribution. 
However, with traditional 
MCMC methods, the samples may be heavily correlated instead of independent 
and may fail to sufficiently explore the 
full space of the distribution (see \cref{fig:bimodal}); 
PT is a method that aims to address these issues.
For a more in-depth review of PT, we refer readers to \cite{surjanovic2022vpt}.

@@

\subsection{Local exploration and communication}
A central data structure in Pigeons is the \texttt{Replica}, a Julia struct 
which we will often refer to in the remainder of this section. 
A single \texttt{Replica} stores a \texttt{state} variable and a \texttt{chain} 
integer, among other entries. 
At the beginning of PT, $N$ \texttt{Replicas} are created, 
one for each distribution on the annealing path, and 
the chain entries in the $N$ replicas are initialized at $1,2,\ldots,N$, respectively. 
For a given \texttt{Replica}, if the \texttt{chain} number is $i$ and the \texttt{state}
is $x$, then this means that the sample corresponding to the $i$-th distribution in 
the sequence $\pi_1, \ldots, \pi_N$ is currently at location $x$.

@@

\subsection{Distributed implementation}
A distributed implementation of PT is shown in \cref{alg:distributed_PT}
and we describe the details of the implementation below.
For simplicity, we present the algorithm from the perspective that the number of machines available 
is equal to the number of \texttt{Replica}s and distributions, $N$. 
However, Pigeons.jl also allows for the more general case where the number of 
machines is not necessarily equal to $N$.

\subsubsection{The \texttt{PermutedDistributedArray}}
\label{sec:permuted_dist_array}
Recall that our theoretical $O(1)$ message size for communication between two machines 
is achieved by exchanging \texttt{chain} indices between \texttt{Replica}s 
instead of their \texttt{state}s. 
However to achieve this low cost a specialized distributed data structure is 
needed to maintain a mapping from chain indices to machine identifiers. 
To motivate it, we start with an illustrative example. 
Suppose we have $N=4$ distributions, chains, replicas, and machines, and that 
machine 1 is exploring chain 2 while machine 4 is exploring chain 3.
At one point, the \texttt{Replica} at \texttt{chain} 2 (machine 1) might need to exchange
\texttt{chain} indices with the \texttt{Replica} that has \texttt{chain} index 3 (machine 4). 
However, a priori it is not clear how machine 1 should know that it should communicate 
with machine 4 because it has no knowledge about the chain indices on the other machines.

\medskip 
To resolve this issue, we introduce a special data structure called a 
\texttt{PermutedDistributedArray}. In the case where the number of replicas is 
equal to the number of available machines, the construction is quite simple
and effectively results in each machine storing one additional integer. 
Considering the same example above, the solution to the problem is to have
machine 1 (\texttt{chain} 2 wanting to communicate with \texttt{chain} 3) 
communicate with \textit{machine} 3. 
Machine 3 stores in its \texttt{dist\_array} variable of type 
\texttt{PermutedDistributedArray} the value 4, which is the machine number that 
stores \texttt{chain} 3. By updating these \texttt{PermutedDistributedArray} 
variables at each communication step, we can ensure that each machine $j$ is aware 
of which machine number currently stores \texttt{chain} $j$. 
Therefore, the machines act as keys in a dictionary for the communication 
permutations.
An illustration of communication between four machines is provided in 
\cref{fig:index_process}.
We note that with a \texttt{PermutedDistributedArray} we make special assumptions 
on how we access and write to the array elements. 
Several MPI processes cooperate, with each machine storing 
data for a slice of this distributed array, and at each time 
step an index of the array is manipulated by exactly one machine. 
Thanks to this, we do not need to resort to global MPI synchronization steps.

\begin{figure*}[t] 
  \centering 
  \begin{minipage}{0.48\textwidth}
    \centering
    \includegraphics[width=0.39\textwidth]{../img/Communication_1_v3.pdf}
    \includegraphics[width=0.59\textwidth]{../img/index_process_1.pdf}
  \end{minipage}
  \begin{minipage}{0.48\textwidth}
    \centering
    \includegraphics[width=0.39\textwidth]{../img/Communication_2_v3.pdf}
    \includegraphics[width=0.59\textwidth]{../img/index_process_2.pdf}
  \end{minipage}
  \begin{minipage}{0.48\textwidth}
    \centering
    \includegraphics[width=0.39\textwidth]{../img/Communication_3_v3.pdf}
    \includegraphics[width=0.59\textwidth]{../img/index_process_3.pdf}
  \end{minipage}
  \begin{minipage}{0.48\textwidth}
    \centering
    \includegraphics[width=0.39\textwidth]{../img/Communication_4_v3.pdf}
    \includegraphics[width=0.59\textwidth]{../img/index_process_4.pdf}
  \end{minipage}
  \caption{
    A summary of communication between four machines with $N=4$ PT chains.
    Circles represent machines with the machine number in the center of the circle. 
    Different colours are also used for different machines.
    Numbers in parentheses represent the \texttt{chain} 
    that is currently being explored by that machine. 
    Arrows indicate communication occuring between machines to exchange \texttt{chain} 
    indices.
    To keep track of which chains are stored on which machine, we introduce the 
    \texttt{dist\_array} of type \texttt{PermutedDistributedArray}, described in 
    \cref{sec:permuted_dist_array}, which is of length $N$. 
    The $j$-th element of \texttt{dist\_array} at a given time step indicates which 
    machine number is storing \texttt{chain} index $j$.
    The bolded curve in the figures to the right indicate the trajectory of the first 
    \texttt{Replica} over the course of each of the communication steps.      
    \textbf{Top left:} the PT replicas are initialized and the first communication step 
    is proposed. At this time step, $\texttt{dist\_array} = [1,2,3,4]$.
    \textbf{Top right:} after the first successful communication step, we now have 
    $\texttt{dist\_array} = [2,1,4,3]$.
    \textbf{Bottom left:} The second communication step is completed and 
    $\texttt{dist\_array} = [2,4,1,3]$.
    \textbf{Bottom right:} The third communication step is completed and 
    $\texttt{dist\_array} = [4,2,3,1]$.}
  \label{fig:index_process}
\end{figure*}

\subsubsection{MPI implementation details}
We use the MPI.jl \cite{byrne2021mpi} package to support communication between machines. 
In  \cref{alg:distributed_PT}, the function \texttt{swap\_stat()} extracts the 
sufficient statistic required by each partner of a swap. The swap
sufficient statistic contains two elements:
(1) a uniformly distributed random number, and (2) the log of the ratio 
$\pi_c(x_t) / \pi_{c'}(x_t)$, up to a normalization constant which may 
depend on $c$ and $c'$ but not $x_t$.  
The function \texttt{transmit()} is used to exchange these statistics 
between the two partners of a proposed swap. In order to make an 
accept-reject decision, the two machines use the same uniform sample (using an arbitrary, fixed 
convention, namely the shared sufficient statistic's uniform from the lowest 
interacting chain index) to make a common swap decision (where the 
acceptance ratio is the sum of the two exchanged log ratios, (2)).

%In our pseudocode in \cref{alg:distributed_PT} we define the MPI-style 
%functions \texttt{send()}, \texttt{receive!()}, 
%and \texttt{waitall()}. 
%The function \texttt{send()} has three arguments in our pseudocode: the first argument 
%is the object to be sent, the second is the machine number to which the object should 
%be sent, and finally the third argument is a unique tag for this specific send/receive 
%request at this time step and on this machine, generated by \texttt{tag()}.
%The \texttt{tag()} function can be any function that allows one to uniquely identify 
%a tag for a given send/receive request on a given machine at any given time step $t$.
%The function \texttt{receive!()} has the same last two arguments as \texttt{send()} 
%except that the first argument 
%specifies the object to which data should be written directly. Finally, 
%\texttt{waitall(requests)} waits for all initialized MPI \texttt{requests} for a given pair 
%of machines to complete.

\medskip 
In \cref{alg:distributed_PT} we also introduce the functions 
\texttt{permuted\_get()} and \texttt{permuted\_set!()}, which operate 
on a  \texttt{PermutedDistributedArray} as described  in \cref{sec:permuted_dist_array}.
Given the current machine's \texttt{dist\_array} and the 
\texttt{partner} chain with which it should communicate, 
\texttt{permuted\_get()} returns the machine number that holds the \texttt{partner} chain. 
Given the current machine's \texttt{dist\_array}, \texttt{chain} number, and machine number $j$,
\texttt{permuted\_set!()} updates the \texttt{PermutedDistributedArray} variables 
with the updated permutation.

@@

      \State $x_t \gets \texttt{local\_exploration}(\pi_\texttt{chain}, x_{t-1})$
      \State $c_t \gets \texttt{chain}$ 
      \If{$\texttt{chain} \in P$}
        \State $\texttt{partner} \gets \texttt{chain}+1$
      \ElsIf{$\texttt{chain}-1 \in P$}
        \State $\texttt{partner} \gets \texttt{chain}-1$
      \Else 
      	\State $\texttt{partner} \gets \texttt{chain}$
      \EndIf
      \State $\texttt{to\_machine} \gets  \texttt{permuted\_get}(\texttt{dist\_array}, \texttt{partner})$
      \State $\texttt{my\_stat} \gets \texttt{swap\_stat}(x_t, $\texttt{chain}, $\texttt{partner} )$  
      \State $\texttt{partner\_stat} \gets \texttt{transmit}(\texttt{my\_stat}, \texttt{to\_machine})$
      \If{$\text{swap\_accepted}(\texttt{my\_stat}, \texttt{partner\_stat})$}
        \State $\texttt{chain} \gets \texttt{partner\_chain}$
      \EndIf
      \State $\texttt{permuted\_set!}(\texttt{dist\_array}, \texttt{chain}, j)$ 
		\EndFor
    \State \Return $\{(x_t, c_t)\}_{t=1}^T$
	\end{algorithmic}
  \caption{Distributed PT on machine $j$ (one replica per machine)}
  \label{alg:distributed_PT}
\end{algorithm}

@@

\begin{figure*}[t]
    \centering
    \begin{minipage}{0.4\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../img/speedup_distributed.pdf}
    \end{minipage}
    \begin{minipage}{0.4\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../img/speedup_parallel.pdf}
    \end{minipage}
    \caption{
        Weak scaling results for PT in both the distributed (MPI, {\bf left}) and parallel settings (Julia threads, {\bf right})  
        with approximate 95\% confidence intervals for the speedup relative to single-thread execution.   
        The blue dotted line represents a hypothetical speedup equal to the 
        number of processes/threads. 
        The red dashed line indicates a speedup of one for reference.
    }
    \label{fig:PT_scaling}
\end{figure*}

@@

We emphasize again that Pigeons supports both shared memory 
parallelism (SMP) and distributed memory parallelism (DMP). However, in certain cases, it 
might be useful to run parallel tempering with  many chains or 
to run several instances of parallel tempering at once. In such cases, 
the DMP setup is the most natural if the requested number of chains is very large. 
Another notable example of the benefit of DMP is for the multi-GPU use case. 
For instance, in some situations the likelihood evaluation of a single chain may 
require its own GPU (e.g., if one is running a Fast Fourier Transform on a GPU). 
Additionally, DMP can be useful when the user's code is not thread safe. 
In such cases, concurrency can still be achieved via DMP.
Our implementation in Pigeons ensures that the 
communication cost in the DMP setup is minimal. In most cases, the 
communication cost is negligible compared to other computations performed on each process.

### 2024-05-28 paper/examples.tex
Pass on the distributed pseudo-code

\subsubsection{Running MPI on a cluster}
Often, MPI is available via a cluster scheduling system. To run MPI over 
several machines:
\begin{enumerate}
    \item In the cluster login node, follow the Pigeons.jl installation instructions
    in our online documentation. 
    \item Start Julia in the login node, and perform a one-time setup by 
    calling \texttt{Pigeons.setup\_mpi()}.
    \item In the Julia REPL running in the login node, run:
\end{enumerate}
\begin{lstlisting}[language = Julia]
pigeons(
    target = TuringLogPotential(model), 
    n_chains = 1_000,
    on = MPI(n_mpi_processes = 1_000, 
             n_threads = 1))
\end{lstlisting}
The code above will start a distributed PT algorithm with 1,000 chains on 1,000 
MPI processes each using one thread.
Note that for the above code chunks involving \texttt{ChildProcess()} and 
\texttt{MPI()} to work, it may be necessary to specify dependencies in their 
function calls.

>>>>

\subsubsection{Running MPI on a cluster}
Often, MPI is available via a cluster scheduling system. To run MPI over 
several machines:
\begin{enumerate}
    \item In the cluster login node, follow the Pigeons.jl installation instructions
    in our online documentation. 
    \item Start Julia in the login node, and perform a one-time setup by 
    calling \texttt{Pigeons.setup\_mpi()}.
    \item In the Julia REPL running in the login node, run:\footnote{In 
    version 0.4.0 of Pigeons, the function \text{MPI} has been renamed \text{MPIProcesses} 
    to avoid a clash with the library \text{MPI.jl}.}
\end{enumerate}
\begin{lstlisting}[language = Julia]
pigeons(
    target = TuringLogPotential(model), 
    n_chains = 1_000,
    on = MPI(n_mpi_processes = 1_000, 
             n_threads = 1))
\end{lstlisting}
The code above will start a distributed PT algorithm with 1,000 chains on 1,000 
MPI processes each using one thread.
Note that for the above code chunks involving \texttt{ChildProcess()} and 
\texttt{MPI()} to work, it may be necessary to specify dependencies in their 
function calls. See \url{https://pigeons.run/stable/mpi/} for details.
